\documentclass[11pt,a4paper]{article}
\usepackage[a4paper,margin=0.5in]{geometry}
\usepackage[T1]{fontenc}
\usepackage[hidelinks]{hyperref}
\usepackage{xcolor}
\usepackage{enumitem}
\usepackage{titlesec}

\pagestyle{empty}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}
\setlist[itemize]{leftmargin=1.1em, label=--, topsep=1pt, itemsep=1pt, parsep=0pt}

\titleformat{\section}{\bfseries\large}{}{0em}{}
\titlespacing*{\section}{0pt}{5pt}{2pt}

\newcommand{\sectionline}{\vspace{-4pt}\hrule\vspace{4pt}}
\newcommand{\blockspace}{\vspace{2pt}}
\newcommand{\projectlink}[2]{\href{#1}{\textcolor{blue}{\textit{#2}}}}
\newcommand{\projecttitle}[1]{{\fontsize{12}{13}\selectfont\textbf{#1}}}
\newcommand{\projectdescspace}{\vspace{0pt}}
\newcommand{\projectstack}[1]{{\footnotesize\itshape #1}}

\begin{document}

\begin{center}
	{\LARGE \textbf{Arif Ashraf}} \\
	\small
	Bengaluru, Karnataka
	\; --- \; \href{mailto:arif18052@gmail.com}{Mail}
	\; --- \; +91 9797012112
	\; --- \; \href{https://www.linkedin.com/in/arif-ashraf-3abb89179}{LinkedIn}
	\; --- \; \href{https://github.com/arifashraf01}{GitHub}
	\; --- \; \href{https://arifashraf01.github.io/3d-portfolio-arif/}{Portfolio}
\end{center}

\section*{Summary}
\sectionline
Final-year Computer Science student with strong foundations in Java, data structures, and backend development.
Experienced in building scalable applications using Django, Spring Boot, and MySQL.
Seeking an SDE role to build high-impact systems.

\blockspace

\section*{Education}
\sectionline
\textbf{SEA College of Engineering and Technology (SEACET), Bengaluru}
\hfill 2022 -- Present \\
BE in Computer Science and Engineering
\hfill CGPA: 8.5/10

\blockspace

\section*{Skills}
\sectionline
\textbf{Languages:} Java, Python, C++ \\
\textbf{Frameworks \& Backend:} Spring Boot, Spring Security, JWT, WebSocket, REST APIs, React \\
\textbf{Databases:} PostgreSQL, MySQL, MongoDB \\
\textbf{Web Technologies:} HTML, CSS, JavaScript \\
\textbf{Tools \& Platforms:} Git, GitHub, GitHub Actions, AWS EC2, Nginx

\blockspace

\section*{Experience}
\sectionline
\textbf{Netpy Technologies} --- Software Developer Intern
\hfill Oct 2025 -- Present
\begin{itemize}
	\item Developed and maintained backend services in Django for a cloud-based e-commerce platform used across core order workflows.
	\item Built and documented 15+ REST APIs for authentication, catalog, and order processing modules.
	\item Implemented OTP login and RBAC across 3 user roles (admin, operations, customer support).
	\item Optimized critical inventory and transaction queries, reducing API response time by approximately 25\%.
	\item Delivered features through PR-based Agile cycles, contributing to weekly release milestones.
\end{itemize}

\blockspace

\section*{Projects}
\sectionline
\projecttitle{DPI Engine --- Deep Packet Inspection System} \hfill \projectlink{https://github.com/arifashraf01/Packet_analyzer}{GitHub} \\
\projectstack{C++ --- Networking --- PCAP Parsing --- Multithreading --- TLS}
\projectdescspace
\normalsize
\begin{itemize}
	\item Built a Deep Packet Inspection engine to parse raw PCAP captures and perform flow-level traffic analysis.
	\item Implemented custom parsers for 4 protocols: Ethernet, IPv4, TCP, and UDP.
	\item Extracted TLS SNI from HTTPS Client Hello packets to enable domain-level traffic identification.
	\item Developed a rule engine supporting 3 enforcement layers: IP, application, and domain blocking.
	\item Designed a multithreaded processing pipeline with thread-safe queues.
\end{itemize}

\blockspace

\projecttitle{Real-Time Chat Application} \hfill \projectlink{https://github.com/arifashraf01/ephemeral-chat-system}{GitHub} \;|\; \projectlink{https://chatapp.stacksense.in}{Live} \\
\projectstack{Java --- Spring Boot --- WebSocket --- REST APIs}
\projectdescspace
\normalsize
\begin{itemize}
	\item Developed and deployed a real-time chat backend using Spring Boot and WebSocket messaging.
	\item Implemented bidirectional communication with sub-second message delivery in local testing.
	\item Designed 10+ REST APIs for user management, chat rooms, and message persistence.
	\item Built backend flows supporting 50+ concurrent user sessions during functional load tests.
\end{itemize}

\blockspace

\projecttitle{Client Project --- Gill Organics} \hfill \projectlink{https://gillorganics.com}{Website} \\
\projectstack{Django --- E-commerce Backend --- REST APIs}
\projectdescspace
\normalsize
\begin{itemize}
	\item Developed backend modules for product catalog, authentication, and order lifecycle workflows.
	\item Built 12+ REST endpoints for product listing, category management, cart, and order placement.
	\item Improved checkout and order-status workflows, reducing manual support dependency for order tracking.
	\item Optimized inventory and transaction queries, improving consistency and response times under peak usage.
	\item Supported integration, QA fixes, and release cycles to deliver production-ready features on schedule.
	\item Added validation and error-handling logic to improve API reliability and reduce failed order operations.
\end{itemize}

\blockspace

\section*{Achievements}
\sectionline
\begin{itemize}
	\item 2nd Prize --- College Hackathon (Innovation Category)
	\item Solved 100+ DSA problems in Java/C++ across arrays, strings, sets, linked lists and maps.
	\item TCS TechBytes --- Reached the Semifinalist stage in a national-level technical competition focused on problem-solving and coding aptitude.
	\item Selected for Inter-College Round of SAP Labs NEXTGRID Hackfest
\end{itemize}

\end{document}
